Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-09 manuscript/paper.Rmd
update

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/svm-r-markdown-templates). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to
yield $n = 19225$ observations on 35 covariates. This sample size was
comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and
2017/2018 survey cycles, respectively. Analyses excluded individuals
with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055),
and body mass index (BMI) or those with BMI \> 25 kg/$m^2$ (overweight)
(n = 5521). Individuals that reported being on anti-hypertensive
medication were also excluded from further analyses (n = 2944).

@@

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". Sleep duration was divided into three groups, which were \< 6
h, 6--8 h, ≥ 8 h respectively, of which 6--8 h was used as the reference
group.

@@

::: {#refs}
:::

>>>>

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
thanks: "Replication files are available on the author's Github account (http://github.com/okutse/sleepBP). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Second Author, Another Uni
- Graduate Student, Graduate School
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to yield $n = 19225$ observations on 35 covariates. This sample size was comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and 2017/2018 survey cycles, respectively. Analyses excluded individuals with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055), and body mass index (BMI) or those with BMI > 25 kg/$m^2$ (overweight) (n = 5521). Individuals that reported being on anti-hypertensive medication were also excluded from further analyses (n = 2944).

@@

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". Sleep duration was divided into three groups, which were < 6
h, 6--8 h, ≥ 8 h respectively, of which 6--8 h was used as the reference
group.

@@
